---
title: "ChicagoCrime"
author: "Pallava Arasu Pari, Rahul Rajesh Munot, Shriya Deshmukh, Deepti Gupta"
date: "August 7, 2018"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This Project is inclined towards developing a linear regression model which would detect likeliness of arrest for a crime conducted in Chicago. 

We used data set from Chicago crime database which is from the following link:
https://data.cityofchicago.org/Public-Safety/Crimes-2001-to-present/ijzp-q8t2


Packages and Libraries

```{r}

#install.packages("GGally")
#install.packages("Rmisc")
#install.packages("lubridate")
#install.packages("ggplot2")

library(GGally)
library(Rmisc)
library(lubridate)
library(ggplot2)

```



Loading the Source file
We already downloaded the source file, we are now loading it
```{r}

setwd("C:/MyRWork/Data/ChicagoCrime")
rawSrcData<-read.csv("Crimes_-_2001_to_present.csv")
nrow(rawSrcData)

```


Select subset of data we require for our analysis. Lets take the data from year 2013 
```{r}
modDS1<-rawSrcData
modDS1<-modDS1[modDS1$Year!="2001",]
modDS1<-modDS1[modDS1$Year!="2002",]
modDS1<-modDS1[modDS1$Year!="2003",]
modDS1<-modDS1[modDS1$Year!="2004",]
modDS1<-modDS1[modDS1$Year!="2005",]
modDS1<-modDS1[modDS1$Year!="2006",]
modDS1<-modDS1[modDS1$Year!="2007",]
modDS1<-modDS1[modDS1$Year!="2008",]
modDS1<-modDS1[modDS1$Year!="2009",]
modDS1<-modDS1[modDS1$Year!="2010",]
modDS1<-modDS1[modDS1$Year!="2011",]
modDS1<-modDS1[modDS1$Year!="2012",]
sort(unique(modDS1$Year))
``` 



Add Different Date Metrics to slice and Dice the crime data
```{r}

modDS2<-modDS1
modDS2$Date <- as.Date(modDS2$Date, "%m/%d/%Y %I:%M:%S %p")
modDS2$Day<-factor(day(as.POSIXlt(modDS2$Date, format="%m/%d/%Y %I:%M:%S %p")))
modDS2$Weekday <- factor(wday(as.POSIXlt(modDS2$Date, format="%m/%d/%Y %I:%M:%S %p"), label = TRUE))
modDS2$Month <- factor(month(as.POSIXlt(modDS2$Date, format="%m/%d/%Y %I:%M:%S %p"), label = TRUE))
modDS2$Year <- factor(year(as.POSIXlt(modDS2$Date, format="%m/%d/%Y %I:%M:%S %p")))
```



Factorize the required variables as categorical variables
```{r}
modDS3<-modDS2
modDS3$Primary.Type<-as.factor(modDS3$Primary.Type)
modDS3$Location.Description<-as.factor(modDS3$Location.Description)
modDS3$Arrest<-as.factor(modDS3$Arrest)
modDS3$Month<-as.factor(modDS3$Month)
modDS3$Weekday<-as.factor(modDS3$Weekday)
modDS3$Year<-as.factor(modDS3$Year)
modDS3$Beat<-as.factor(modDS3$Beat)
modDS3$District<-as.factor(modDS3$District)
```


remove whitespaces
```{r}
modDS4<-modDS3

modDS4<-modDS4[modDS4$Primary.Type!="",]
modDS4<-modDS4[modDS4$Location.Description!="",]
modDS4<-modDS4[modDS4$Arrest!="",]
modDS4<-modDS4[modDS4$Beat!="",]
modDS4<-modDS4[modDS4$Weekday!="",]
modDS4<-modDS4[modDS4$Month!="",]
modDS4<-modDS4[modDS4$District!="",]
```


Remove missing values
```{r}
modDS5<-modDS4
modDS5<-na.omit(modDS5)
```


removing duplicates and cleansing the data
```{r}
#removing duplicates
modDS6<-modDS5
modDS6<-modDS6[!duplicated(modDS6$'Case.Number',modDS6$Date),]

#cleansing the data
modDS6$Primary.Type <- gsub("(.*)NON(.*)CRIMINAL(.*)","NON-CRIMINAL",modDS6$Primary.Type)
modDS6$Location.Description <- gsub("(.*)AIRPORT(.*)","AIRPORT",modDS6$Location.Description)
modDS6$Location.Description <- gsub("AUTO(.*)","AUTO",modDS6$Location.Description)
modDS6$Location.Description <- gsub("CHA(.*)","CHA",modDS6$Location.Description)
modDS6$Location.Description <- gsub("CHURCH(.*)","CHURCH",modDS6$Location.Description)
modDS6$Location.Description <- gsub("CLEAN(.*)","CLEANERS",modDS6$Location.Description)
modDS6$Location.Description <- gsub("COLLEGE(.*)","COLLEGE",modDS6$Location.Description)
modDS6$Location.Description <- gsub("CTA(.*)","CTA",modDS6$Location.Description)
modDS6$Location.Description <- gsub("DRIVEWAY(.*)","DRIVEWAY",modDS6$Location.Description)
modDS6$Location.Description <- gsub("GARAGE(.*)","GARAGE",modDS6$Location.Description)
modDS6$Location.Description <- gsub("GAS(.*)","GAS STATION",modDS6$Location.Description)
modDS6$Location.Description <- gsub("GOVERNMENT(.*)","GOVERNMENT BUIDING",modDS6$Location.Description)
modDS6$Location.Description <- gsub("HOSPITAL(.*)","HOSPITAL",modDS6$Location.Description)
modDS6$Location.Description <- gsub("HOTEL(.*)","HOTEL",modDS6$Location.Description)
modDS6$Location.Description <- gsub("NURSING(.*)","NURSING HOME",modDS6$Location.Description)
modDS6$Location.Description <- gsub("OTHER(.*)TRA(.*)","OTHER TRANSPORTATION",modDS6$Location.Description)
modDS6$Location.Description <- gsub("PARKING(.*)","PARKING",modDS6$Location.Description)
modDS6$Location.Description <- gsub("POOL(.*)","POOL ROOM",modDS6$Location.Description)
modDS6$Location.Description <- gsub("RESIDE(.*)","RESIDENCE",modDS6$Location.Description)
modDS6$Location.Description <- gsub("SCHOOL(.*)","SCHOOL",modDS6$Location.Description)
modDS6$Location.Description <- gsub("TAVERN(.*)","TAVERN",modDS6$Location.Description)
modDS6$Location.Description <- gsub("TAXI(.*)","TAXI CAB",modDS6$Location.Description)
modDS6$Location.Description <- gsub("VACANT(.*)","VACANT",modDS6$Location.Description)
modDS6$Location.Description <- gsub("VEHICLE(.*)","VEHICLE",modDS6$Location.Description)
modDS6$Location.Description <- gsub("BARBER(.*)","BARBER SHOP",modDS6$Location.Description)


sort(unique(modDS6$Primary.Type))
sort(unique(modDS6$Location.Description))
```



Data Exploration : here we tried to understand the trends and patterns occuring in 
the data

```{r}

modDS6DE <- modDS6

# Removing year 2018 data as it is only from january-june, the graphs might get 
# impacted when they are plotted monthwise 
modDS6DE<-modDS6DE[modDS6DE$Year!="2018",]



#Question - What is the pattern of crime over the recent years?
DSCountWithYear <- data.frame(Year = modDS6DE$Year, Arrest = modDS6DE$Arrest)
ggplot(DSCountWithYear, aes(Year,fill = factor(Arrest))) +stat_count(width = 0.5)
#Observation - The crime seems to be decreasing and specifically the arrest seems to be decreasing


#Question - What is the pattern of crime when analysed monthwise?
DSCountWithTime <- data.frame(Month = modDS6DE$Month, Arrest = modDS6DE$Arrest)
ggplot() + geom_bar(aes(x=Month, y=Arrest, fill=factor(Arrest)), size=1,
                           data = DSCountWithTime, stat="identity")
#Observation - Crime is supposed to highest in July, August, Low in winters and lowest
# in the month of february



# Question - What is the patterns of crime over the weekdays?
DSCountWeekdays <- aggregate(Arrest~Weekday,FUN=length,data=modDS6DE)
ggplot() + geom_bar(aes(y = Arrest, x = Weekday, fill=Weekday), size=0.5,
                           data = DSCountWeekdays, stat="identity")
# Crimes are occuring maximum during friday, saturday



#Question - What is the pattern of crime district wise?
DSCountWithDistrict <- data.frame(District = modDS6DE$District, Arrest = modDS6DE$Arrest)
ggplot(DSCountWithDistrict, aes(District,fill = factor(Arrest))) +stat_count(width = 0.5)
#Observation - District 8 and 11 have the highest number and 20 has the lowest



# Question - What are the most prone and less prone crimes occuring in the city of chicago?
DSCountPrimaryType1 <- data.frame(Primary.Type = modDS6DE$Primary.Type, Arrest = modDS6DE$Arrest)
ggplot(DSCountPrimaryType1, aes(Primary.Type, fill = factor(Arrest))) +stat_count(width = 0.5) + theme(axis.text.x = element_text(angle = 90, hjust = 1))


DSCountPrimaryType <- aggregate(Arrest~Primary.Type + Weekday,FUN=length,data=modDS6DE)
summary(DSCountPrimaryType)
DSCountPrimaryType$Level <- ifelse(DSCountPrimaryType$Arrest > 7000, "High", "Low")

ggplot(DSCountPrimaryType, aes(y= log(Arrest), x=Primary.Type, fill = Level) )+ 
    geom_bar(position="dodge", stat="identity") +     coord_flip()
# Observation - The first graph had really low values which were not observable, 
# which is why we took the log values which shows the clear trend. The most popular 
# crimes are Theft, battery, burglary and narcotics


# Question - Analyse the pattern of top crimes occuring over the weekdays?

g1<- ggplot(subset(DSCountPrimaryType, Primary.Type=='THEFT'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for theft on weekdays")

g2<- ggplot(subset(DSCountPrimaryType, Primary.Type=='BATTERY'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for battery on weekdays")

g3<- ggplot(subset(DSCountPrimaryType, Primary.Type=='NARCOTICS'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for narcotics on weekdays")

g4<- ggplot(subset(DSCountPrimaryType, Primary.Type=='CRIMINAL DAMAGE'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for criminal damage on weekdays")

g5<- ggplot(subset(DSCountPrimaryType, Primary.Type=='ROBBERY'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for robbery on weekdays")

g6<- ggplot(subset(DSCountPrimaryType, Primary.Type=='MOTOR VEHICLE THEFT'), 
    aes(y=Arrest, x=Weekday, fill = Arrest), size = 1) + 
    geom_bar( stat="identity") +
    ggtitle("Number of Arrests for motor vehicle theft on weekdays")

multiplot(g1, g2, g3, g4, g5, g6, cols=2)
# Observation - all the top crimes shows a same pattern of having high occurrences 
# during friday and saturdays


```



Deriving Correlation among the variables which can be logically related
```{r}

modDS7Cor <- modDS3
modDS7Cor<-modDS7Cor[modDS7Cor$Year!="2018",]


# Below columns are definitely not logically related to data, e.g. x coordinates and 
# y coordinates are generally very precise values which will have very less chance
# of being duplicate. ID, Case Number will be unique for every crime occurance. So
# the values which will be unique for almost all the rows should be eliminated


modDS7Cor$ID <- NULL
modDS7Cor$Case.Number<-NULL
modDS7Cor$Date<-NULL
modDS7Cor$X.Coordinate <- NULL
modDS7Cor$Y.Coordinate <- NULL
modDS7Cor$Updated.On<-NULL
modDS7Cor$Latitude<-NULL
modDS7Cor$Longitude<-NULL
modDS7Cor$Location<-NULL
modDS7Cor$Block<-NULL
modDS7Cor$IUCR <- NULL
modDS7Cor$Description<-NULL

head(modDS7Cor)
unique(sort(modDS7Cor$FBI.Code))

modDS7Cor$Location.Description = factor(modDS7Cor$Location.Description,levels =c('ABANDONED BUILDING','AIRCRAFT','AIRPORT','ALLEY','ANIMAL HOSPITAL','APARTMENT','APPLIANCE STORE','ATHLETIC CLUB','ATM (AUTO','AUTO','BANK','BAR OR TAVERN','BARBER SHOP','BASEMENT','BOAT/WATERCRAFT','BOWLING ALLEY','BRIDGE','CAR WASH','CEMETARY','CHA','CHURCH','CLEANERS','CLUB','COIN OPERATED MACHINE','COLLEGE','COMMERCIAL / BUSINESS OFFICE','CONSTRUCTION SITE','CONVENIENCE STORE','CREDIT UNION','CTA','CURRENCY EXCHA','DAY CARE CENTER','DELIVERY TRUCK','DEPARTMENT STORE','DRIVEWAY','DRUG STORE','ELEVATOR','EXPRESSWAY EMBANKMENT','FACTORY/MANUFACTURING BUILDING','FARM','FEDERAL BUILDING','FIRE STATION','FOREST PRESERVE','GANGWAY','GARAGE','GAS STATION','GOVERNMENT BUIDING','GROCERY FOOD STORE','HALLWAY','HIGHWAY/EXPRESSWAY','HORSE STABLE','HOSPITAL','HOTEL','HOUSE','JAIL / LOCK-UP FACILITY','LAGOON','LAKEFRONT/WATERFRONT/RIVERBANK','LAUNDRY ROOM','LIBRARY','LIQUOR STORE','MEDICAL/DENTAL OFFICE','MOTEL','MOVIE HOUSE/THEATER','NEWSSTAND','NURSING HOME','OFFICE','OTHER','OTHER TRANSPORTATION','PARK PROPERTY','PARKING','PAWN SHOP','POLICE FACILITY/VEH PARKING','POOL ROOM','PORCH','RAILROAD PROPERTY','RESIDENCE','RESTAURANT','RETAIL STORE','RIVER BANK','ROOMING HOUSE','SAVINGS AND LOAN','SCHOOL','SIDEWALK','SMALL RETAIL STORE','SPORTS ARENA/STADIUM','STAIRWELL','STREET','TAVERN','TAXI CAB','TRUCK','VACANT','VEHICLE','VESTIBULE','WAREHOUSE','YARD','YMCA'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96))
modDS7Cor$Location.Description = as.numeric(modDS7Cor$Location.Description)


modDS7Cor$Primary.Type = factor(modDS7Cor$Primary.Type,levels =c('ARSON','ASSAULT','BATTERY','BURGLARY','CONCEALED CARRY LICENSE VIOLATION','CRIM SEXUAL ASSAULT','CRIMINAL DAMAGE','CRIMINAL TRESPASS','DECEPTIVE PRACTICE','GAMBLING','HOMICIDE','HUMAN TRAFFICKING','INTERFERENCE WITH PUBLIC OFFICER','INTIMIDATION','KIDNAPPING','LIQUOR LAW VIOLATION','MOTOR VEHICLE THEFT','NARCOTICS','NON-CRIMINAL','OBSCENITY','OFFENSE INVOLVING CHILDREN','OTHER NARCOTIC VIOLATION','OTHER OFFENSE','PROSTITUTION','PUBLIC INDECENCY','PUBLIC PEACE VIOLATION','ROBBERY','SEX OFFENSE',
'STALKING','THEFT','WEAPONS VIOLATION'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31))
modDS7Cor$Primary.Type = as.numeric(modDS7Cor$Primary.Type)


modDS7Cor$FBI.Code = factor(modDS7Cor$FBI.Code,levels =c("01A","01B","02","03","04A","04B","05","06","07","08A","08B" ,"09","10","11","12","13","14","15","16","17","18","19","20","22","24","26"),  labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26))
modDS7Cor$FBI.Code = as.numeric(modDS7Cor$FBI.Code)

modDS7Cor$Arrest = factor(modDS7Cor$Arrest,levels = c('false','true'),labels = c(0,1))
modDS7Cor$Arrest = as.numeric(modDS7Cor$Arrest)

modDS7Cor$Domestic = factor(modDS7Cor$Domestic,levels = c('false','true'),labels = c(0,1))
modDS7Cor$Domestic = as.numeric(modDS7Cor$Domestic)


modDS7Cor$Weekday<-factor(modDS7Cor$Weekday,levels = c('Sun','Mon','Tue','Wed','Thu','Fri','Sat'),labels = c(0,1,2,3,4,5,6))
modDS7Cor$Weekday = as.numeric(modDS7Cor$Weekday)

modDS7Cor$Month<-factor(modDS7Cor$Month,levels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec'),labels = c(0,1,2, 3,4,5,6,7,8,9,10,11))
modDS7Cor$Month = as.numeric(modDS7Cor$Month)


modDS7Cor$Beat = as.numeric(modDS7Cor$Beat)
modDS7Cor$District = as.numeric(modDS7Cor$District)
modDS7Cor$Year = as.numeric(modDS7Cor$Year)
modDS7Cor$Day = as.numeric(modDS7Cor$Day)

str(modDS7Cor)


cor(modDS7Cor)
ggcorr(modDS7Cor,label = TRUE,label_alpha = TRUE)



```


Exploratory analysis concluded that Primary.Type,Location.Description,Arrest,Month,Weekday,Year,Beat,District are the influential variables
```{r}
modDS7<-modDS6
modDS7<-subset(modDS7,select = c('Primary.Type','Location.Description','Arrest','Beat','Weekday','Month','District','Year'))

```


Data Modelling
Change categorical values to numbers
```{r}
modDS8<-modDS7
sort(unique(modDS8$Location.Description))

modDS8$Location.Description = factor(modDS8$Location.Description,levels =c('ABANDONED BUILDING','AIRCRAFT','AIRPORT','ALLEY','ANIMAL HOSPITAL','APARTMENT','APPLIANCE STORE','ATHLETIC CLUB','ATM (AUTO','AUTO','BANK','BAR OR TAVERN','BARBER SHOP','BASEMENT','BOAT/WATERCRAFT','BOWLING ALLEY','BRIDGE','CAR WASH','CEMETARY','CHA','CHURCH','CLEANERS','CLUB','COIN OPERATED MACHINE','COLLEGE','COMMERCIAL / BUSINESS OFFICE','CONSTRUCTION SITE','CONVENIENCE STORE','CREDIT UNION','CTA','CURRENCY EXCHA','DAY CARE CENTER','DELIVERY TRUCK','DEPARTMENT STORE','DRIVEWAY','DRUG STORE','ELEVATOR','EXPRESSWAY EMBANKMENT','FACTORY/MANUFACTURING BUILDING','FARM','FEDERAL BUILDING','FIRE STATION','FOREST PRESERVE','GANGWAY','GARAGE','GAS STATION','GOVERNMENT BUIDING','GROCERY FOOD STORE','HALLWAY','HIGHWAY/EXPRESSWAY','HORSE STABLE','HOSPITAL','HOTEL','HOUSE','JAIL / LOCK-UP FACILITY','LAGOON','LAKEFRONT/WATERFRONT/RIVERBANK','LAUNDRY ROOM','LIBRARY','LIQUOR STORE','MEDICAL/DENTAL OFFICE','MOTEL','MOVIE HOUSE/THEATER','NEWSSTAND','NURSING HOME','OFFICE','OTHER','OTHER TRANSPORTATION','PARK PROPERTY','PARKING','PAWN SHOP','POLICE FACILITY/VEH PARKING','POOL ROOM','PORCH','RAILROAD PROPERTY','RESIDENCE','RESTAURANT','RETAIL STORE','RIVER BANK','ROOMING HOUSE','SAVINGS AND LOAN','SCHOOL','SIDEWALK','SMALL RETAIL STORE','SPORTS ARENA/STADIUM','STAIRWELL','STREET','TAVERN','TAXI CAB','TRUCK','VACANT','VEHICLE','VESTIBULE','WAREHOUSE','YARD','YMCA'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96))


modDS8$Primary.Type = factor(modDS8$Primary.Type,levels =c('ARSON','ASSAULT','BATTERY','BURGLARY','CONCEALED CARRY LICENSE VIOLATION','CRIM SEXUAL ASSAULT','CRIMINAL DAMAGE','CRIMINAL TRESPASS','DECEPTIVE PRACTICE','GAMBLING','HOMICIDE','HUMAN TRAFFICKING','INTERFERENCE WITH PUBLIC OFFICER','INTIMIDATION','KIDNAPPING','LIQUOR LAW VIOLATION','MOTOR VEHICLE THEFT','NARCOTICS','NON-CRIMINAL','OBSCENITY','OFFENSE INVOLVING CHILDREN','OTHER NARCOTIC VIOLATION','OTHER OFFENSE','PROSTITUTION','PUBLIC INDECENCY','PUBLIC PEACE VIOLATION','ROBBERY','SEX OFFENSE',
'STALKING','THEFT','WEAPONS VIOLATION'),labels=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31))


modDS8$Arrest = factor(modDS8$Arrest,levels = c('false','true'),labels = c(0,1))

modDS8$Weekday<-factor(modDS8$Weekday,levels = c('Sun','Mon','Tue','Wed','Thu','Fri','Sat'),labels = c(0,1,2,3,4,5,6))

modDS8$Month<-factor(modDS8$Month,levels = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec'),labels = c(0,1,2, 3,4,5,6,7,8,9,10,11))

head(modDS8)

```
# lets create some dummy variables to list features and arrests
```{r}

modDS9<-modDS8

# After facing error in knn model with large data set, i reduced the training data set to 50000
modDS9<-data.frame(modDS9)
index<-sample(1:nrow(modDS9),50000)
modDS9<-modDS9[index,]

#lets list the number of arrest happend in the dataset and use it in the training.
arrest_factor=modDS9$Arrest

#lets create dummy variables as for all combination of features and provide arrest factor for those
dummy_features<-model.matrix(Arrest~.-1,data = modDS9)

#Lets split the data set with respect to row index, we can use the same to match the dummy arrest
set.seed(1234)
split_index=sample(1:2, length(modDS9$Arrest),replace= T, prob = c(.8,.2))

```
#lets determine the training and testing data set based on the split critera
```{r}
#determinind the training and testing data set
train_data=dummy_features[split_index==1,]
test_data=dummy_features[split_index==2,]

#determine the training and testing arrest factor with the split index
train_arrest_factor=arrest_factor[split_index==1]
test_arrest_factor=arrest_factor[split_index==2]

```

#lets use knn model to dertmine
#KNN Model:
```{r}
#got error with too many ties in knn. so reduced the sample size

require(class)
model<-knn(train=train_data, test=test_data, cl=train_arrest_factor, k=144)
```

```{r}
#Accuracy Rate
sum(model==test_arrest_factor)/length(model)

#Confusion Matrix
table(model, test_arrest_factor)

```